|

### 2016-05-15 Benchmark/iTRAQ4-Benchmark/itraq-benchmark.Rmd
benchmark

@@

```{r}
# Original data
dim(qnt.id)         # From MSXML File e-value < 50
dim(msexp.sp)       # From PNNL (all)
qnt.merged <- merge(qnt.id, msexp.sp, by.x = "scan number(s)", by.y = "ScanNumber", all.x = T, all.y = F)
dim(qnt.merged)     # Merged Data (left Join)
head(qnt.merged[,c(cols.sp, cols.p3)])
```

The error/differences (results from MsnBase - results from PNNL):
```{r}
q.Error <- qnt.merged[,c("scan number(s)", "pepseq", "ms-gf:evalue")]
q.Error <- cbind(q.Error, "errIon114"= qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114, "errIon115"=qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115, "errIon116"=qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116, "errIon117"=qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)

head(q.Error[order(q.Error$`ms-gf:evalue`),])
boxplot(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
summary(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
```
# References

>>>>

Some peptides do not have complete (all ions) quantified. Only peptides with complete ions measurements are retained. 
```{r}
## Before filtered
dim(exprs(qnt))
summary(exprs(qnt))
## After filtered
dim(exprs(qnt.f))
summary(exprs(qnt.f))
```

@@

```{r}
# Original data
dim(qnt.id)         # From MSXML File < e-value treshold
dim(msexp.sp)       # From PNNL (all)
qnt.merged <- merge(qnt.id, msexp.sp, by.x = "scan number(s)", by.y = "ScanNumber", all.x = T, all.y = F)
dim(qnt.merged)     # Merged Data (left Join)
head(qnt.merged[,c(cols.sp, cols.p3)])
```

The error/differences (results from MsnBase - results from PNNL) / results from PNNL:

```{r}
q.Error <- qnt.merged[,c("scan number(s)", "pepseq", "ms-gf:evalue")]
q.Error <- cbind(q.Error, "errIon114"= abs(qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114)/qnt.merged$Ion_114, "errIon115"=abs(qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115)/qnt.merged$Ion_115, "errIon116"=abs(qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116)/qnt.merged$Ion_116, "errIon117"=abs(qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)/qnt.merged$Ion_117)
#q.Error <- cbind(q.Error, "errIon114"= apply(qnt.merged[,c("iTRAQ4.114","Ion_114") ],2,relError), "errIon115"=apply(qnt.merged[,c("iTRAQ4.115","Ion_115") ],2,relError), "errIon116"=apply(qnt.merged[,c("iTRAQ4.116","Ion_116") ],2,relError), "errIon117"=apply(qnt.merged[,c("iTRAQ4.117","Ion_117") ],2,relError))

head(q.Error[order(q.Error$`ms-gf:evalue`),])
boxplot(log10(q.Error[,c("errIon114","errIon115","errIon116","errIon117")]), main="Error (log10) scale.")
## Error (Real Values)
summary(log10(q.Error[,c("errIon114","errIon115","errIon116","errIon117")]))
```
# References
